Workshop Instructions: Reproducible Scientific Manuscripts

### 2024-05-16 Instructions.qmd
added readme instruction

In this part of the workshop, you will integrate all of the skills, you acquired in the previous lessons.
You will firstly execute a self-contained minimal example that is provided in this repository.
Secondly, you will recreate the minimal example using all the components provided in the folder "02_practice".
Thirdly, you will create your own first reproducible manuscript based on a conventional manuscript you already have.
And finally, you can use the checklist provided in the "03_supplement" folder to go over your project and see how many reproducibility measure you applied.

@@

4. Open the newly created ".Rproj" file in RStudio.
5. Within the R Project, create a new Quarto document:
- Click on File > New File > Quarto Document...
6. Replace the content of the new Quarto document with the provided text.
7. Modify the fiel paths to ensure that all provided files (data, bibliography, etc.) are correctly imported and referenced in your Quarto document.
8. Execute the Quarto document to generate your practice manuscript.

>>>>

In this part of the workshop, you will integrate all of the skills, you acquired in the previous lessons.
You will firstly execute a self-contained minimal example that is provided in this repository.
Secondly, you will recreate the minimal example using all the components provided in the folder "02_Practice".
Thirdly, you will create your own first reproducible manuscript based on a conventional manuscript you already have.
And finally, you can use the checklist provided in the "03_Supplement" folder to go over your project and see how many reproducibility measures you have applied.

@@

4. Open the newly created ".Rproj" file in RStudio.
5. Within the R Project, create a new Quarto document:
- Click on File > New File > Quarto Document...
6. Replace the content of the new Quarto document with the provided text.
7. Modify the fiel paths to ensure that all provided files (data, bibliography, etc.) are correctly imported and referenced in your Quarto document.
8. Execute the Quarto document to generate your practice manuscript.
9. Add a README.md file to the "02_Practise" folder and describe, which steps users have to to in order to execute your Minimal Example.
